---
title: "Untitled"
format: html
editor: visual
---

**Package Installation**

```{r}
install.packages("tidyverse")
library(tidyverse)
install.packages("ggplot2")
library(ggplot2)
install.packages("dslabs")
library(dslabs)
install.packages("dplyr")
library(dplyr)
data(mpg)

```

**9.2.1 Exercise Part 1**

```{r}
ggplot(mpg)+geom_point(aes(hwy/10^6,displ)) +
  geom_point(aes(x = displ, y = hwy, color = "pink"), shape = 17)  
   

```

**9.2.1 Exercise Part 2**

ggplot(mpg) + geom_point(aes(x = displ, y = hwy, color = "blue"))

**The code did not produce a plot with blue points because after the "ggplot(mpg) +," there is no geom_point aes plotting for the x and y axis.**

**9.2.1 Exercise Part 3 and 4**

```{r}
ggplot(mpg)+geom_point(aes(hwy/10^6,displ)) +
  geom_point(aes(x = displ, y = hwy, color = "pink"), shape = 17), stroke = 3)
```

**The stroke aesthetic (I assume) gives the entire every graphed point an outline, I believe it would only work with filled shapes.**

**I think that aesthetic would apply because all that changes is the fact that the aesthetic is not used on a variable name.**
